### 2020-02-21 ChapterResults/chapterResults.tex
Added: Correctness experiment diagram and other tweaks to Results chapter

\subsection{Varying Factors}
Experiments were carried out to demonstrate the effects of varying each aura calculation factor on the correctness of collisions between objects. The purpose of these experiments is to demonstrate that collisions in AP are always correct if the three factors that determine aura size remain within respective tolerance, i.e. there are no late or missed collisions. In addition, if the aura calculation is correct, we expect to see late collisions begin to occur as soon as tolerances are exceeded. If errors do not occur as soon as the tolerances are exceeded, this is evidence that the aura radius is too large. Large auras can lead to reduced performance in AP, therefore auras that are only as large as needed to be, for the given tolerance, are desirable to maximise performance.

In this experiment two servers were used with one sphere being created on each server. The two spheres were given starting positions so the two would collide at a point when one of the spheres is intersecting the server region boundary, thus creating the most likely situation for spheres collide with each other in the first time-step after being migrated; this is necessary as AP can only lead to late or missed collisions when at least one sphere involved in the collision has just migrated (received since the last physics time-step). This is because non-migrating spheres behave the same as spheres in a centralised solution, therefore only collisions that involve a sphere that has just migrated are considered in the experiment results.

There are three factors that are used to determine aura size: speed; latency; and frame-time. In order to demonstrate the effect each factor has on collision correctness, one aura factor is varied per experiment and the other two factors are set to equal the tolerance values. For example, speed is varied, the latency between the servers is set to equal the latency tolerance value and the frame-time of each server is set to equal the frame-time tolerance value. The non-varied factors are set to equal the tolerance values as exceeding the tolerance value in one factor can be compensated for by having a value below the tolerance in a different factor. For example, the latency may exceed the tolerance by $5ms$, but the frame-time could be more than $5ms$ below the frame-time tolerance and the collision would still be expected to be correctly handled by AP.

@@

\subsection{Thrashing}
In addition to recording the number of collisions that resulted in thrashing, the number of times an object thrashed between servers was also measured. The number of times thrashed is determined by measuring the number of migrations away from the server that the collisions takes place on, before the collision takes place. A histogram of the number of occurrences against the number of times thrashed is shown in Fig. \ref{fig_ThrashingHistogram}. For this histogram, data from the Frame-Time $33.33ms$ experiment is used, as this provides the largest sample of thrashing. Fig. \ref{fig_ThrashingHistogram} demonstrates that the most frequent number of times thrashed is 1, by a large margin followed by a downward trend.

@@

\subsubsection{Evaluation}
As the speed increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsSpeedLow}, \ref{fig_RatioVsSpeedMid} and \ref{fig_RatioVsSpeedHigh}. When speed is below the speed tolerance, late collisions do not exceed 10\%. This 10\% can be accounted for by false-positives. Once above the speed tolerance, the proportion of late collisions increases immediately, which is predicted by the aura calculation. Missed collisions begin to occur when speed exceed $80ms^{-1}$ in the $48ms^{-1}$ experiment, this is due to objects travelling so quickly, the objects completely pass one another, missing the collision entirely.

@@

As the latency increases, the proportion of late collisions to correct collisions increases, as shown in Fig. \ref{fig_RatioVsLatencyHigh}. However, Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyLow} do not show this relationship. In the $2ms$ latency tolerance experiment, late collisions do not exceed $20\%$, which can be accounted for by false-positives. The aura calculation predicts that late collisions should start occurring once $3ms$ has been exceeded, however, this is not observed, as the proportion does not increase above what would be expected for false-positives.
In the $8ms$ latency tolerance experiment, late collisions do not exceed $2\%$, which can be accounted for by false-positives. This remains the case even when the tolerance is exceeded. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached, which this experiment does not reach, therefore no late collisions outside of false-positives are expected. In the $16ms$ latency tolerance experiment, late collisions do not exceed $3\%$ below the tolerance, which can be accounted for by false-positives. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached. In Fig. \ref{fig_RatioVsLatencyHigh} we see the proportion of errors increase from $20ms$ and above, however, it does not exceed the expected false-positive proportion until $25ms$ latency is reached.
%TODO: Re-run latency experiment, larger sample size?

@@

As frame-time increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyMid}, however in \ref{fig_RatioVsLatencyHigh} the sample size is small above the tolerance line due to the high occurrences of thrashing and so the relationship in this experiment can not be deduced. For the $8ms$ and $15ms$ experiments the late collisions do not exceed 10\% and these can be accounted for by false-positives. In the $8ms$ frame-time tolerance experiment, late collisions are not expected to occur until $16ms$ frame-time, based on the aura size. Late collisions do not exceed $20\%$ and these can all be accounted for by false-positives. In the $15ms$ frame-time tolerance experiment, late collisions exceed $20\%$ once $16ms$ latency is exceeded as predicted by the aura size and increase to over $75\%$ at $30ms$ latency.
In the final frame-time tolerance experiment using $32ms$ frame-time tolerance, late collisions only occur for frame-times of $64ms$. The aura calculation predicts that late collisions should begin to occur as soon as $32ms$ frame-time is exceeded, however, due to the low sample size, as a result of the high occurrences of thrashing, the plot does not accurately represent any relationship between frame-time and proportion of late collisions.

@@

The varying factors experiments demonstrate that the aura calculation is correct for all aura tolerance factors. For each varied factor, for all three tolerance values chosen, below the tolerance value, the mean + two standard deviations lies under the maximum penetration time expected on a centralised simulation, with only a small number of exceptions discussed above. These experiments also demonstrate the relationship between increasing the tolerance values and amount of thrashing expected to occur. There are no missed collisions, with the exception of the speed experiments, which have significantly fewer than $1\%$ misses below the tolerance and $1.12\%$ misses above the tolerance. Once factors increase above their respective tolerance values, late collisions begin to occur and the more the factors are exceeded, the number and magnitude of errors increase. This demonstrates the correctness of the aura calculation in AP.
%Therefore, we have shown that if the aura calculation factors remain within their respective tolerances, erroneous collisions will be small in magnitude and rare in number. %TODO: Summary Table: Row for each factor: Number of collisions below tolerance, Percentage of errors below tolerance, Mean error below tolerance

@@

\subsection{Varying Packet-Loss}

>>>>

\subsection{Experiment- Varying Factors}
Experiments were carried out to demonstrate the effects of varying each aura calculation factor on the correctness of collisions between objects. The purpose of these experiments is to demonstrate that collisions in AP are always correct if the three factors that determine aura size remain within respective tolerance, i.e. there are no late or missed collisions. In addition, if the aura calculation is correct, we expect to see late collisions begin to occur as soon as tolerances are exceeded. If errors do not occur as soon as the tolerances are exceeded, this is evidence that the aura radius is too large. Large auras can lead to reduced performance in AP, therefore auras that are only as large as needed to be, for the given tolerance, are desirable to maximise performance.

In order t rigorously test the hypothesis "Can real-time physics simulations remain correct when scaled?", a `worst-case' scenario was used for the experiments, in which two objects are moving directly towards each other and collide while one of the objects is intersecting the boundary between servers. In this experiment two servers were used with one sphere being created on each server. The two spheres were given starting positions so the two would collide at a point when one of the spheres is intersecting the server region boundary, thus creating the most likely situation for spheres collide with each other in the first time-step after being migrated; this is necessary as AP can only lead to late or missed collisions when at least one sphere involved in the collision has just migrated (received since the last physics time-step). This is because non-migrating spheres behave the same as spheres in a centralised solution, therefore only collisions that involve a sphere that has just migrated are considered in the experiment results.

\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{CorrectnessExperiment}
	\caption{Correctness Experiment setup. The setup is the `worst-case' scenario, in which two objects are moving directly towards each other and collide while one of the objects is intersecting the boundary between servers.}
	\label{fig_CorrectnessExperiment}
\end{figure}

There are three factors that are used to determine aura size: speed; latency; and frame-time. In order to demonstrate that collisions always remain correct when within their tolerance, even under worsening conditions and the effect each factor has on collision correctness, one aura factor is varied per experiment and the other two factors are set to equal the tolerance values. For example, speed is varied, the latency between the servers is set to equal the latency tolerance value and the frame-time of each server is set to equal the frame-time tolerance value. The non-varied factors are set to equal the tolerance values as exceeding the tolerance value in one factor can be compensated for by having a value below the tolerance in a different factor. For example, the latency may exceed the tolerance by $5ms$, but the frame-time could be more than $5ms$ below the frame-time tolerance and the collision would still be expected to be correctly handled by AP.

@@

\subsubsection{Thrashing}
In addition to recording the number of collisions that resulted in thrashing, the number of times an object thrashed between servers was also measured. The number of times thrashed is determined by measuring the number of migrations away from the server that the collisions takes place on, before the collision takes place. A histogram of the number of occurrences against the number of times thrashed is shown in Fig. \ref{fig_ThrashingHistogram}. For this histogram, data from the Frame-Time $33.33ms$ experiment is used, as this provides the largest sample of thrashing. Fig. \ref{fig_ThrashingHistogram} demonstrates that the most frequent number of times thrashed is 1, by a large margin followed by a downward trend.

@@

\subsubsection{Evaluation - Speed}
As the speed increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsSpeedLow}, \ref{fig_RatioVsSpeedMid} and \ref{fig_RatioVsSpeedHigh}. When speed is below the speed tolerance, late collisions do not exceed 10\%. This 10\% can be accounted for by false-positives. Once above the speed tolerance, the proportion of late collisions increases immediately, which is predicted by the aura calculation. Missed collisions begin to occur when speed exceed $80ms^{-1}$ in the $48ms^{-1}$ experiment, this is due to objects travelling so quickly, the objects completely pass one another, missing the collision entirely.

@@

\subsubsection{Evaluation - Latency}
As the latency increases, the proportion of late collisions to correct collisions increases, as shown in Fig. \ref{fig_RatioVsLatencyHigh}. However, Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyLow} do not show this relationship. In the $2ms$ latency tolerance experiment, late collisions do not exceed $20\%$, which can be accounted for by false-positives. The aura calculation predicts that late collisions should start occurring once $3ms$ has been exceeded, however, this is not observed, as the proportion does not increase above what would be expected for false-positives.
In the $8ms$ latency tolerance experiment, late collisions do not exceed $2\%$, which can be accounted for by false-positives. This remains the case even when the tolerance is exceeded. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached, which this experiment does not reach, therefore no late collisions outside of false-positives are expected. In the $16ms$ latency tolerance experiment, late collisions do not exceed $3\%$ below the tolerance, which can be accounted for by false-positives. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached. In Fig. \ref{fig_RatioVsLatencyHigh} we see the proportion of errors increase from $20ms$ and above, however, it does not exceed the expected false-positive proportion until $25ms$ latency is reached.
%TODO: Re-run latency experiment, larger sample size?

@@

\subsubsection{Evaluation - Frame-Time}
As frame-time increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyMid}, however in \ref{fig_RatioVsLatencyHigh} the sample size is small above the tolerance line due to the high occurrences of thrashing and so the relationship in this experiment can not be deduced. For the $8ms$ and $15ms$ experiments the late collisions do not exceed 10\% and these can be accounted for by false-positives. In the $8ms$ frame-time tolerance experiment, late collisions are not expected to occur until $16ms$ frame-time, based on the aura size. Late collisions do not exceed $20\%$ and these can all be accounted for by false-positives. In the $15ms$ frame-time tolerance experiment, late collisions exceed $20\%$ once $16ms$ latency is exceeded as predicted by the aura size and increase to over $75\%$ at $30ms$ latency.
In the final frame-time tolerance experiment using $32ms$ frame-time tolerance, late collisions only occur for frame-times of $64ms$. The aura calculation predicts that late collisions should begin to occur as soon as $32ms$ frame-time is exceeded, however, due to the low sample size, as a result of the high occurrences of thrashing, the plot does not accurately represent any relationship between frame-time and proportion of late collisions.

@@

\subsubsection{Summary}
The varying factors experiments demonstrate that the aura calculation is correct for all aura tolerance factors. For each varied factor, for all three tolerance values chosen, below the tolerance value, the mean + two standard deviations lies under the maximum penetration time expected on a centralised simulation, with only a small number of exceptions discussed above. These experiments also demonstrate the relationship between increasing the tolerance values and amount of thrashing expected to occur. There are no missed collisions, with the exception of the speed experiments, which have significantly fewer than $1\%$ misses below the tolerance and $1.12\%$ misses above the tolerance. Once factors increase above their respective tolerance values, late collisions begin to occur and the more the factors are exceeded, the number and magnitude of errors increase. This demonstrates the correctness of the aura calculation in AP.
%Therefore, we have shown that if the aura calculation factors remain within their respective tolerances, erroneous collisions will be small in magnitude and rare in number. %TODO: Summary Table: Row for each factor: Number of collisions below tolerance, Percentage of errors below tolerance, Mean error below tolerance

@@

\subsection{Experiment - Varying Packet-Loss}
